Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-18 paper.tex
Put two figures side by side

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
\paragraph{Random Unreal}
The training set is sampled randomly with no restriction, that is,
regardless of the file generation time. This method will be used as a
baseline for comparison with other methods, although it is not
realistic. Figure~\ref{fig:Random-Unreal-Sample-Training-set} represents 
a training set sampled using this method.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training}
  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.3.}
  \label{fig:Random-Unreal-Sample-Training-set}
\end{figure}

% 2. columns
\paragraph{Complete Columns}
The training set is sampled by randomly selecting complete columns in
the matrix, that is, complete subject executions. The last selected
column might be incomplete to meet the exact training ratio. This 
method is realistic: it corresponds to a situation where the 
collaborative filtering method will predict the reproducibility in the 
remaining subjects from the subjects in the training set. 
Figure~\ref{fig:Columns-Sample-Training-set} represents a training set 
sampled using this method.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training}
  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.3.}
  \label{fig:Columns-Sample-Training-set}
\end{figure}

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training}
  \caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.3.}
  \label{fig:Rows-Sample-Training-set}
\end{figure}

\paragraph{Random Subjects} This method builds the 
training set by selecting the next generated file of a random subject 
until the training ratio is reached. The next generated file of a 
subject is the file with the lowest index in this subject that has not 
been already selected in the training set. This method is realistic as 
files are sampled according to their production timestamps. 
Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training}
  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.3.}
  \label{fig:Uniform-S-Sample-Training-set}
\end{figure}

\paragraph{Random File Numbers (Uniform)}
The 
number of files selected in every subject is randomly selected in a 
uniform distribution with parameters a and b where a and b are set as follows: \ldots{}
This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.

\paragraph{Random File Numbers (Triangular)}
The number of files selected in every subject is randomly selected in a triangular distribution
with parameters a, b and c where a, b and c are set as follows: \ldots{}
This ununiform distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a:  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.
\todo{Add a Figure.}
\item Smallest-a: In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
\todo{Add a Figure.}
\end{enumerate}

>>>>

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
\paragraph{Random Unreal}
The training set is sampled randomly with no restriction, that is,
regardless of the file generation time. This method will be used as a
baseline for comparison with other methods, although it is not
realistic. Figure~\ref{fig:Random-Unreal-Sample-Training-set} represents 
a training set sampled using this method.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.4.}
  \label{fig:Random-Unreal-Sample-Training-set}
\end{figure}

% 2. columns
\paragraph{Complete Columns}
The training set is sampled by randomly selecting complete columns in
the matrix, that is, complete subject executions. The last selected
column might be incomplete to meet the exact training ratio. This 
method is realistic: it corresponds to a situation where the 
collaborative filtering method will predict the reproducibility in the 
remaining subjects from the subjects in the training set. 
Figure~\ref{fig:Columns-Sample-Training-set} represents a training set 
sampled using this method.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.4.}
  \label{fig:Columns-Sample-Training-set}
\end{figure}

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
  		\caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.4.}
  		\label{fig:Rows-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
		\caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
  		\label{fig:Uniform-S-Sample-Training-set}
	\end{subfigure}
\end{figure}

\paragraph{Random Subjects} This method builds the 
training set by selecting the next generated file of a random subject 
until the training ratio is reached. The next generated file of a 
subject is the file with the lowest index in this subject that has not 
been already selected in the training set. This method is realistic as 
files are sampled according to their production timestamps. 
Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
  \label{fig:Uniform-S-Sample-Training-set}
\end{figure}

\paragraph{Random File Numbers (Uniform)}
The 
number of files selected in every subject is randomly selected in a 
uniform distribution with parameters a and b where a and b are set as follows: \ldots{}
This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01. 
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
  \caption{Sample training set obtained with the Random File Numbers (Uniform) method with a training ratio of 0.4.}
  \label{fig:Diagonal-Sample-Training-set}
\end{figure}

\paragraph{Random File Numbers (Triangular)}
The number of files selected in every subject is randomly selected in a triangular distribution
with parameters a, b and c where a, b and c are set as follows: \ldots{}
This ununiform distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a:  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
  \caption{Sample training set obtained with the Random File Numbers (Triangular-L) method with a training ratio of 0.4.}
  \label{fig:triangular-L-Sample-Training-set}
\end{figure}
\item Smallest-a: In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
  \caption{Sample training set obtained with the Random File Numbers (Triangular-S) method with a training ratio of 0.4.}
  \label{fig:triangular-S-Sample-Training-set}
\end{figure}
\end{enumerate}
